\documentclass[12pt]{letter}


\usepackage{hyperref}
\usepackage{fullpage}


\longindentation=0pt 

\signature{Marvin Smith}
\address{Marvin Smith\\207 Imperial Blvd\\ Reno, NV, 89503}

\begin{document}

\begin{letter}{}

\opening{Dear Drone Deploy,}


I am writing to you to express my interest in the Python Software Engineer position. I believe that I have 
the requisite knowledge and experience to provide valuable contributions to your company.


Currently, I am a Software Engineer with the Sierra Nevada Corporation in Sparks, NV. My primary focuses are in 
photogrammetry and distributed computing for the Intelligence, Surveillance, and Reconnaissance (ISR) division. 
Specifically, I develop image processing software for military UAS applications, most notably, Gorgon Stare. 
Most of my work has me writing in C++, however I do extensive prototyping, testing, and system administration in Python. 
The primary software libraries I use are GDAL and OpenCV for both Python and C++. 
Other packages I use in my work include MPI, GeographicLib, libLAS, and Eigen.


Prior to working at the Sierra Nevada Corporation, I was able to gain notable experience while interning at the NASA Ames 
Research Center in Mountain View, CA. For two summers, I worked on satellite imagery of the Lunar and Martian surface. 
This required developing C++ software for the NASA Vision Workbench which was run on the Pleiades Supercomputer. 
In addition to valuable internships during college, I was an Air Force avionics technician.   
As an avionics technician, I repaired and maintained C-130 Navigation, Communication, and Electronic Counter-Measure equipment. 


I have a strong passion for cartography, image processing, and navigation.
These interests drive me to participate in other projects. I have contributed code to the OpenCV
project. Specifically, I created the drivers in the new OpenCV 3.0 release to incorporate GDAL to the 
OpenCV image IO library. Finally, I was a technical reviewer for two OpenCV books, one focusing on C++ 
and the other on Python.


I believe that I have a wide array of skills to offer as well as the drive and ability to pick up new ones. Thank you very much for your time.


\closing{Sincerely,}
\end{letter}

\end{document}


